Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-03 method.tex
editorial about lloid
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@920 ccdd05d5-56c1-461a-bf98-85f6876523b4
Reworked last part of section 2
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@922 ccdd05d5-56c1-461a-bf98-85f6876523b4

\subsection{The \lloid\ method}

@@

From the combination of transformations to the compact binary templates defined
in equation \eqref{eq:time-sliced-templates} and \eqref{eq:svddecomp} we define
the early warning filter output accumulated up to time slice $s$ as,
%
% orthogonal decomposition filtering
%
\begin{equation}
	\rho_i^s [k] =%
		% Reconstruction
		\underbrace{
			\sum_{\mathclap{l=0}}^{\mathclap{L^s-1}} v_{il}^s \sigma_l^s
		}_\textrm{\clap{reconstruction}}
		% Orthogonal FIR filter
		\overbrace{
			\sum_{\mathclap{n=0}}^{\mathclap{N^s-1}} u_l^s[n] x^s[k-n]
		}^\textrm{\clap{orthogonal {\sc fir} filters}}
		% Plus ...
		+
		% Interpolation SNR
		\underbrace{
			\left(H^\uparrow \rho_i^{s+1}\right)[k]
		}_\textrm{\clap{{\sc snr} from previous time slices}}
\end{equation}
%
%
\FIXME{This quantity is related to the early warning SNR by the normalization
of the partial filter defined by the present time slice.}  Figure
\ref{fig:pipeline} describes the computation of the \SNR\ and early warning
\SNR\ schematically.
%
%
\begin{figure}[htbp]
	\includegraphics{figures/lloid-diagram.pdf}
	\caption{\label{fig:pipeline} Schematic of LLOID pipeline illustrating
signal flow.  Circles with arrows represent interpolation
\protect\includegraphics{figures/upsample-symbol.pdf} or decimation
\protect\includegraphics{figures/downsample-symbol.pdf}.  Circles with plus
signs represent summing junctions
\protect\includegraphics{figures/adder-symbol.pdf}.  Squares
\protect\includegraphics{figures/fir-symbol.pdf} stand for FIR filters.  Sample
rate decreases from the top of the diagram to the bottom.  In this diagram each
time slice contains three \fir\ filters that are linearly combined to produce
four output channels.  In a typical pipeline the number of \fir\ filters is
much less than the number of output channels.}
\end{figure}
%
%
The signal flow diagram drawn in figure \ref{fig:pipeline} contains several
distinct stages and parallel branches.  The stages are decimation, filtering
the data against the orthogonal templates, reconstruction of the original
template basis, interpolation and accumulation of the early warning and final
{\SNR}.

>>>>

\editorial{if we are gonna stick with lloid we should define it}
\subsection{The \lloid\ method}

@@

From the combination of transformations to the compact binary templates defined
in equation \eqref{eq:time-sliced-templates} and \eqref{eq:svddecomp} we define
the early warning filter output accumulated up to time slice $s$ as,
%
% orthogonal decomposition filtering
%
\begin{equation}
	\rho_i^s [k] =%
		% Reconstruction
		\underbrace{
			\sum_{\mathclap{l=0}}^{\mathclap{L^s-1}} v_{il}^s \sigma_l^s
		}_\textrm{\clap{reconstruction}}
		% Orthogonal FIR filter
		\overbrace{
			\sum_{\mathclap{n=0}}^{\mathclap{N^s-1}} u_l^s[n] x^s[k-n]
		}^\textrm{\clap{orthogonal {\sc fir} filters}}
		% Plus ...
		+
		% Interpolation SNR
		\underbrace{
			\left(H^\uparrow \rho_i^{s+1}\right)[k]
		}_\textrm{\clap{{\sc snr} from previous time slices}}
\end{equation}
%
%
\FIXME{This quantity is related to the early warning SNR by the normalization
of the partial filter defined by the present time slice.}
%
%
\begin{figure}[htbp]
	\includegraphics{figures/lloid-diagram.pdf}
	\caption{\label{fig:pipeline} Schematic of LLOID pipeline illustrating
signal flow.  Circles with arrows represent interpolation
\protect\includegraphics{figures/upsample-symbol.pdf} or decimation
\protect\includegraphics{figures/downsample-symbol.pdf}.  Circles with plus
signs represent summing junctions
\protect\includegraphics{figures/adder-symbol.pdf}.  Squares
\protect\includegraphics{figures/fir-symbol.pdf} stand for FIR filters.  Sample
rate decreases from the top of the diagram to the bottom.  In this diagram each
time slice contains three \fir\ filters that are linearly combined to produce
four output channels.  In a typical pipeline the number of \fir\ filters is
much less than the number of output channels.}
\end{figure}
%
%
The signal flow diagram in figure~\ref{fig:pipeline} illustrates how this
recursion relation can be realized as a multirate filter network with outputs for
each of the early warning \SNR{}s.
